\section{Introduction}\label{sec:introduction}

Electricity prices are increasingly exposed to weather and renewable generation.
Temperature affects demand, while wind and solar production affect both the level
and the intraday shape of spot prices. Energy contracts written on such markets
therefore carry hybrid risk, since their value depends on the joint behavior of
electricity prices and physical factors that are non-traded or only partially
traded.

This paper develops an empirical CARMA framework for these joint risks. We first
remove deterministic seasonal patterns from German day-ahead prices,
temperature, wind capacity factors, and solar capacity factors. The resulting
stochastic factors are then modeled with continuous-time autoregressive
moving-average dynamics, which provide a state-space representation for
calibration, dependence estimation, and pricing.

The preprocessing is factor-specific because the deterministic component differs
across markets and weather variables. Electricity prices contain calendar and
intraday effects, temperature has smooth daily and annual cycles, and wind
capacity factors are naturally treated through a logit transformation. Solar
requires an additional clear-sky normalization before the latent logit
transformation, as night hours and moving sunrise and sunset times induce
deterministic boundary effects.

The contribution is threefold. First, we build a consistent preprocessing
pipeline for electricity, temperature, wind, and solar data. Second, we calibrate
marginal CARMA models and recover their driving noise, allowing heavy-tailed
Levy specifications when Gaussian innovations are insufficient. Third, we use
the calibrated factors to estimate price-weather and price-renewable dependence
channels and to price energy contracts exposed to these joint risks.

The paper is organized as follows. \Cref{sec:deseasonalization} describes the
data transformations and the construction of the stochastic factors.
\Cref{sec:marginal-carma-calibration} presents the marginal CARMA calibration
and driver diagnostics. \Cref{sec:coupling-calibration} estimates the dependence
channels. \Cref{sec:pricing} discusses the pricing implementation, and
\Cref{sec:conclusion} concludes.
